Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-20 VMCAI-revised-version/final.tex
effectivity

	\noindent	
	where TM$_j$ is the $j$-th Turing machine (in a classical enumeration)
	which moreover begins
by writing the integer $j$ on its tape,	
	and consider additionnally the function $g : \N^2 \to \N^2$ defined by $g(n,k) = (n+1,k)$. 
	The
	transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ 
	is a $\post$-effective $\omega^2$-WSTS with strong compatibility
	and
	has the property that
	it is
	$\mathop{\uparrow} (1,1)$-resilient
	iff TM$_j$ halts on input $j$,
	since $(1,1)$ is coverable from $(0,0)$
	iff TM$_j$ halts on input $j$. 
	Hence there is no Turing machine which correctly determines 
	resilience and halts whenever its input is a
	WSTS.
Hence resilience for $\omega^2$-WSTS with strong compatibility is undecidable.\qed
\end{proof}
 Let us remark that the transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ in the previous proof is not $\post$-ideal-effective
	nor $\pred$-effective.

>>>>

	\noindent	
	where TM$_j$ is the $j$-th Turing machine (in a classical enumeration)
	which moreover begins
by writing the integer $j$ on its tape,	
	and consider additionnally the function $g : \N^2 \to \N^2$ defined by $g(n,k) = (n+1,k)$. 
	The
	transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ 
	is a $\post$-effective $\omega^2$-WSTS with strong compatibility
	and
	has the property that
	it is
	$\mathop{\uparrow} (1,1)$-resilient
	iff TM$_j$ halts on input $j$,
	since $(1,1)$ is coverable from $(0,0)$
	iff TM$_j$ halts on input $j$. 
	Hence there is no Turing machine which correctly determines 
	resilience and halts whenever its input is a
	WSTS.
Hence resilience for $\omega^2$-WSTS with strong compatibility is undecidable.\qed
\end{proof}
 Let us remark that the transition system 
	$S_j = (\N^2, \{f_j, g\}, \leq)$ in the previous proof is not $\post$-ideal-effective
	nor $\pred$-basis-effective.
